---
title: "Descriptives_Render"
author: "Anissa Hyde"
date: "`r Sys.Date()`"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Packages
```{r message=FALSE, warning=FALSE}
library(glmmTMB)
library(readr)
library(dplyr)
library(gtsummary)
library(sjPlot)
library(performance)
library(DHARMa)
library(tidyr)
library(ggeffects)
library(scales)
```

```{r message=FALSE, warning=FALSE}
period_inputv6 <- read_csv("period_inputv6.csv", 
    col_types = cols(...1 = col_skip()))
```

```{r include=FALSE}
period_inputv6$County<-as.character(period_inputv6$County)
period_inputv6$Commuting.Zone<-as.character(period_inputv6$Commuting.Zone)
period_inputv6$Density<-as.factor(period_inputv6$Density)
period_inputv6$Built<-as.factor(period_inputv6$Built)
period_inputv6$Built<-relevel(period_inputv6$Built,ref = "Before 1950")
period_inputv6$Density<-relevel(period_inputv6$Density, ref = "Moderate and High Density(Suburban and Urban)")

stats <- c(
  "Mean (SD)" = "{mean} ({sd})",
  "Median (IQR)" = "{median} ({IQR})"
)
period_inputv6$Shoreline<-as.factor(period_inputv6$Shoreline)
```

# Table 2: Gulf Wide Descriptive for Gulf Wide Coverage Model
```{r}
theme_gtsummary_compact()

global<- purrr::imap(
  stats,
  ~period_inputv6 %>%
    tbl_summary(
      include =  c("Claims",
                   "Coverage",
                   "Income",
                   "Black",
                   "Hispanic",
                   "Renters",
                   "SFHA",
                   "Risk.Diff",
                   "Built",
                   "Density",
                   "Shoreline"),
       label =  c(Claims ~ "Response: Claims", 
                 Coverage ~ "Vulnerability: Insurance Coverage",
                 Black ~ "Vulnerability: % Black Population", 
                 Hispanic ~ "Vulnerability : % Hispanic Population", 
                 Income ~ "Vunerability: Median Household Income",
                 Renters ~ "Vulnerability: % Renter Occupied",
                 SFHA ~ "Risk: SFHA", 
                 Risk.Diff ~ "Risk: Risk Difference",
                Density ~ "Urban Form: Density Category",
                Shoreline ~ "Shoreline County",
                Built ~ "Urban Form: Median House Age"),
      statistic = list(all_continuous() ~ .x),
      missing = "no") %>%
     modify_header(all_stat_cols() ~ stringr::str_glue("**{.y}**"))
) %>%
  tbl_merge(tab_spanner = FALSE) %>%
  modify_footnote(all_stat_cols() ~ NA) %>%
     modify_caption("**Table 2. Gulf Wide Characteristics**") %>%
  bold_labels()

global
```
# Gulf Wide Coverage Model 
```{r warning=FALSE}
g.coverage <-glmmTMB(Coverage ~ Density +
                                scale(Income) + 
                                scale(Black) + 
                                scale(Hispanic) + 
                                scale(Renters) +
                                #scale(Flood.Factor) +
                                scale(SFHA) +
                                scale(Risk.Diff)+
                                Built +
                                Shoreline +
                                T +
                              (1 |Commuting.Zone:County),
                                dispformula = ~1 ,
                                ziformula = ~1,
                                data = period_inputv6,
                              family = ziGamma(link = "log"),
                     control=glmmTMBControl(optCtrl=list(iter.max=1e6,
                                                         eval.max=1e6)))
```

```{r}
par(mar=c(2,2,2,2))
gresids<-simulateResiduals(g.coverage, n=3000)
plot(gresids)

```

```{r}
plot_model(g.coverage)
```

Gulf Wide Insurance Claims

Notes. Details like labels will come soon

```{r}
g.claims <-glmmTMB(Claims ~ Density +
                       scale(Income) + 
                       scale(Black) + 
                       scale(Hispanic) + 
                       scale(Renters) +
                       #scale(Flood.Factor) +
                       scale(SFHA) +
                      scale(Risk.Diff) +
                       Built +
                      Coverage +
                       Shoreline +
                       T +
                       (1 |Commuting.Zone:County),
                       # (1 | Time.Period),
                     # ziformula = ~1,
                      data = period_inputv6, 
                      family = nbinom2(link = "log"),
                     control=glmmTMBControl(optCtrl=list(iter.max=1e6,
                                                         eval.max=1e6)))
```


```{r}
par(mar=c(2,2,2,2))
gresids<-simulateResiduals(g.claims, n=3000)
plot(gresids)

```



#Extract Exposed Counties

To identify the most exposed counties in our study area we are going to extract our geographical random effect estimates to see which county has the most influence on exposure

```{r}

random<-ranef(g.claims) #Extract the random effect information

random<-as.data.frame(random) # Necessary

claims.ranef<-random %>%
  dplyr::select(grp, condval) %>%
  dplyr:: rename("claim_estimate" = "condval") %>%
  separate(grp,into  = c( "Commuting.Zone","County"), sep = ":")%>%
  na.omit()
```
Join them to the Gulf Wide set to capture covariates
```{r}

period_inputv7<-left_join(period_inputv6,claims.ranef,by  = c("Commuting.Zone","County"))

e.claim<-period_inputv7 %>% filter(claim_estimate >= 0.71) # Third quartile
```
# Exposed County Descriptives 
```{r}
theme_gtsummary_compact()

exposed<- purrr::imap(
  stats,
  ~e.claim %>%
    tbl_summary(
      include =  c("Claims", "Coverage","Income","Black","Hispanic","Renters","SFHA","Flood.Factor","Risk.Diff","Density","Built", "Shoreline"),
      statistic = list(all_continuous() ~ .x),
      missing = "no",
      label =  c(Claims ~ "Response: Claims", 
                 Coverage ~ "Vulnerability: Insurance Coverage",
                 Black ~ "Vulnerability: % Black Population", 
                 Hispanic ~ "Vulnerability : % Hispanic Population", 
                 Income ~ "Vunerability: Median Household Income",
                 Renters ~ "Vulnerability: % Renter Occupied",
                 SFHA ~ "Risk: SFHA", 
                 Flood.Factor ~ "Risk: % Moderate - Severe Flood Factor Score",
                 Risk.Diff ~ "Risk: Flood Factor -  SFHA",
                  Density ~ "Urban Form: Density Category",
                 Built ~ "Urban Form: Median House Age",
                 Shoreline ~ "Shoreline County")) %>%
     modify_header(all_stat_cols() ~ stringr::str_glue("**{.y}**"))
) %>%
  tbl_merge(tab_spanner = FALSE) %>%
  modify_footnote(all_stat_cols() ~ NA) %>%
  bold_labels()

tbl_merge(tbls=list(global,exposed), tab_spanner = c("Global", "Exposed")) %>%
  modify_caption("**Table 1. Descriptives**") %>% 
  bold_labels()
```

```{r}
hist(e.claim$Claims)
```

# Exposed Models

Coverage 
```{r}
e.coverage <-glmmTMB(Coverage  ~ Density +
                                scale(Income) + 
                                scale(Black) + 
                                scale(Hispanic) + 
                                scale(Renters) +
                                #scale(Flood.Factor) +
                                scale(SFHA) +
                                scale(Risk.Diff)+
                                Built +
                                #scale(Coverage)+
                                Shoreline +
                                T +
                                (1 |County),
                                ziformula = ~1, 
                                dispformula = ~1 ,
                                data = e.claim,
                              family = ziGamma(link = "log"),
                     control=glmmTMBControl(optCtrl=list(iter.max=1e6,
                                                         eval.max=1e6)))
```
Claims
```{r}
e.claims <-glmmTMB(Claims ~ Density +
                       scale(Income) + 
                       scale(Black) + 
                       scale(Hispanic) + 
                       scale(Renters) +
                       #scale(Flood.Factor) +
                       scale(SFHA) +
                       scale(Risk.Diff) +
                       Built +
                       Coverage+
                       Shoreline +
                       T +
                       (1 |County),
                       # (1 | Time.Period),
                     # ziformula = ~1,
                      data = e.claim, 
                      family = nbinom2(link = "log"),
                     control=glmmTMBControl(optCtrl=list(iter.max=1e6,
                                                         eval.max=1e6)))
```
# Regression Tables
```{r}
Claims<- tab_model(g.coverage,g.claims,e.coverage,e.claims,show.intercept = TRUE,
                      show.icc = TRUE, 
                      show.aic = TRUE,
                      show.p = FALSE,
                      show.zeroinf = FALSE,
                      p.style = "scientific_stars",
                      dv.labels = c("Gulf Coverage","Gulf Claims ","Exposed Coverage","Exposed Claims"),
                      order.terms = c(7,8,3,6,4,5,1,2,11,9,10,12,13))

Claims

```

#Plot Models 


Plot 1: Coverage Estimates Gulf Wide and Exposed

```{r}
plot_models(g.coverage,e.coverage,
            m.labels = c("Gulf Wide Coverage", "Exposed County Coverage"),
         axis.labels = c(
   "Time Period", "Shoreline","Homes Built After 1989", "Homes Built between 1970-1989","Homes Built Between 1950-1969","Risk Difference","SFHA","Renters","Hispanic","Black","Median Income","Rural Area","Suburban and Urban Areas"),
  show.values = FALSE, 
  show.p = FALSE, 
  p.shape = TRUE
)
```

Plot 2: Claims Estimates Gulf Wide and Exposed

```{r}
plot_models(g.claims,e.claims,
            m.labels = c("Gulf Wide Claims", "Exposed County Claims"),
         axis.labels = c(
   "Time Period", "Shoreline","Homes Built After 1989", "Homes Built between 1970-1989","Homes Built Between 1950-1969","Risk Difference","SFHA","Renters","Hispanic","Black","Median Income","Rural Area","Suburban and Urban Areas", "Insurance Coverage"),
  show.values = FALSE, 
  show.p = FALSE, 
  p.shape = TRUE
)
```

Plot 3: Random Effects 

```{r}
plot_model(e.claims, type = "re") 
# Here I want to use the county names. Adding it to my to do
```

plot 3: Trying out Predicted Plots

example here
```{r}
plot_model(e.coverage,type = "pred",terms =c("Black","T") )
```

another example
Note to adjust labels 
```{r}
plot_model(e.claims,type = "pred",terms =c("scale_coverage","Density") )
```

another example
```{r}
plot_model(e.claims,type = "pred",terms =c("Income","Density","SFHA") )
```

